---
title: "DR analysis"
output: html_document
---

```{r}
source('~/Documents/python-projects/Datathon-DR/scr/R/help.R')
```

```{r load data, warning=FALSE, echo=FALSE, message=FALSE}
library(readr)
basic_info <- read_csv("~/Documents/python-projects/Datathon-DR/data/data0111/basic_info.csv")
# for variable: weight gain brfore rrt perday, if weight gain equals 0, set it to 0
basic_info$weight_gain_before_rrt_perday[which(basic_info$weight_gain_before_rrt == 0)] <- 0
# age above 300 need to convert
basic_info$age[basic_info$age >= 300] <- 90
basic_info[, c("add_drug_therapy", "change_drug_therapy", "rrt")][is.na(basic_info[, c( "add_drug_therapy", "change_drug_therapy", "rrt")])] <- 0

# survival data
survival.data <- read_csv("~/Documents/python-projects/Datathon-DR/data/data0111/survival.csv")[, -1]
survival.data <- merge(survival.data, basic_info[, c('deathtime', 'hadm_id')], by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
survival.data$deathtime <- as.character(survival.data$deathtime)
survival.data$death[!is.na(survival.data$deathtime)] <- 1
survival.data$death[is.na(survival.data$deathtime)] <- 0

# remove timestamp data
basic_info <- basic_info[, names(basic_info) %in% c('subject_id', 'admittime', 'dischtime', 'deathtime', 'first_icu_intime', 'last_icu_outtime', 'diuretic_resis_date', 'diuretic_resis_date', 'maxdose_date', 'get_better_date', 'rrt_charttime') == FALSE]
# convert binary variable to factor
basic_info$gender[which(basic_info$gender == 'F')] <- 0
basic_info$gender[which(basic_info$gender == 'M')] <- 1
basic_info[, c(3, 4, 7, 8, 9, 11)] <- lapply(basic_info[, c(3, 4, 7, 8, 9, 11)], as.factor)

# drug use data 
druguse <- read_csv("~/Documents/python-projects/Datathon-DR/data/data0111/druguse.csv")[, -1]
druguse[, c(2:18)] <- lapply(druguse[, c(2:18)], as.factor)

# nosocomial data by caoyang
nosocomial <- read_csv("~/Documents/python-projects/Datathon-DR/data/data0111/nosocomial.csv")[, -c(1, 3:5)]
nosocomial[is.na(nosocomial)] <- 0
nosocomial[, c(2:4)] <- lapply(nosocomial[, c(2:4)], as.factor)

# fluid load data
fluidload <- read_csv("~/Documents/python-projects/Datathon-DR/data/data0111/fluidload.csv")[, -1]

# vital data
vital <- read_csv("~/Documents/python-projects/Datathon-DR/data/data0111/vital.csv")[, -1]

# lab test
lab <- read_csv("~/Documents/python-projects/Datathon-DR/data/data0111/lab.csv")[, -c(14, 27, 40)]
lab[, c(1:49)] <- lapply(lab[, c(1:49)], as.numeric)

```

```{r merge data, warning=FALSE, echo=FALSE, message=FALSE}
data.raw <- merge(basic_info, druguse, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, fluidload, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, nosocomial, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, vital, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, lab, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, survival.data, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
# write.csv(data.raw, '~/Desktop/survival.csv')
```

###Preprocess -- missing values
* 1. ) several patients may have wrong weight values, since they are no-RRT patients, remove them entirly
* 2. ) cvp have many missing values( > 863/1271), so do urine_acid, bnp and base excess(this one exclude admission), better remove them before analysis.
* 3. ) And the third timestamp(get better date) have about a half missing data, for more then 500 no-rrt patients can't find a urine increase time according to the definition. This may cause bias, but analysis below will still include these variables.

```{r warning=FALSE, echo=FALSE, message=FALSE}
# final dataset
# remove cvp, urine acid, bnp and base excess(not adm)
data.std <- data.raw[, names(data.raw) %in% c('cvp_adm', 'cvp_dr', 'cvp_therapy', 'cvp_dis', 'urine_acid_adm', 'urine_acid_dr', 'urine_acid_therapy', 'urine_acid_dis', 'bnp_adm', 'bnp_dr', 'bnp_therapy', 'bnp_dis', 'base_excess_dr', 'base_excess_therapy', 'base_excess_dis', 'diuretic_drg_start') == FALSE]
data.std$readmit30 <- ifelse(data.std$readmit_gap <= 30, 1, 0)
data.std$readmit30 <- ifelse(is.na(data.std$readmit_gap), 0, data.std$readmit30)
data.std$readmit30 <- as.factor(data.std$readmit30 )
data.std$readmit90 <- ifelse(data.std$readmit_gap <= 90, 1, 0)
data.std$readmit90 <- ifelse(is.na(data.std$readmit_gap), 0, data.std$readmit90)
data.std$readmit90 <- as.factor(data.std$readmit90 )

# split training set and validation set(75% 25%)
# train.data <- data.std[sample(1046, 785), ]
# valid.data <- anti_join(data.std, train.data)
# save data
# write.csv(train.data, '~/Documents/python-projects/Datathon-DR/data/processed/train_data.csv')
# write.csv(valid.data, '~/Documents/python-projects/Datathon-DR/data/processed/valid_data.csv')
```

###1. Baseline characteristics of the entire cohort and the validation cohort, stratified by rrt

```{r warning=FALSE, echo=FALSE, message=FALSE}
# create baseline summary
library(tableone)
catvars <- c("age", "gender", "height", "weight_adm","bmi", "bbr", "inotropes_vasopressor", "acei", "mra", "vasodilator", "ischemic_heart_disease", "cardiomyopathies", "valvular_disease", "atrial_fibrilation", "hyperlipidemia", "hypertension", "diabetes", "sleep_disordered_breathing", "renal_failure", "anemia", "infection", "alcohol_abuse", "hr_adm", "sbp_adm", "dbp_adm", "spo2_adm", "tem_adm", "gfr_adm", "bnp_adm", "base_excess_adm", "hco3_adm", "ph_adm", "urine_acid_adm", "hemoglobin_adm", "albumin_adm", "potassium_adm", "sodium_adm", "creatinine_adm", "bun_adm", 'readmit30', 'readmit90') 
# the entire cohort
test.table <- CreateTableOne(vars=catvars, strata = "rrt", data = data.std)
a <- print(test.table, quote = TRUE)[, -4]
g1 <- paste('Non RRT (n=', a[1,1], ')')
g2 <- paste('RRT (n=', a[1,2], ')')
colnames(a) <- c(g1, g2, 'p-value')
a <- a[-1, ]
# write.csv(a, '~/Documents/python-projects/Datathon-DR/report/baseline_analysis_entire.csv')

# the validation cohort
test.table <- CreateTableOne(vars=catvars, strata = "rrt", data = valid.data)
b <- print(test.table, quote = TRUE)[, -4]
g1 <- paste('Non RRT (n=', b[1,1], ')')
g2 <- paste('RRT (n=', b[1,2], ')')
colnames(b) <- c(g1, g2, 'p-value')
b <- b[-1, ]
# write.csv(b, '~/Documents/python-projects/Datathon-DR/report/baseline_analysis_valid.csv')
```

###2. Characteristics of fluid value and outcomes

```{r}
catvars <- c("los_hos", "los_icu", "hospital_expire_flag", "add_drug_therapy", "change_drug_therapy", "fluid_overload_to_rrt", "daily_fluid_overload_to_rrt", "urine_output_to_rrt", "daily_uo_to_rrt", "total_input_to_discharge", "total_output_to_discharge", "fluid_overload_to_dis", "urine_output_to_dis") 
# entire cohort
test.table <- CreateTableOne(vars=catvars, strata = "rrt", data = data.std)
a <- print(test.table, quote = TRUE)[, -4]
g1 <- paste('Non RRT (n=', a[1,1], ')')
g2 <- paste('RRT (n=', a[1,2], ')')
colnames(a) <- c(g1, g2, 'p-value')
a <- a[-1, ]
# write.csv(a, '~/Documents/python-projects/Datathon-DR/report/outcomevariable_summary_entire.csv')

# valid.data <- read.csv('~/Documents/python-projects/Datathon-DR/data/processed/valid_data.csv')
# valid.data$change_drug_therapy <- as.factor(valid.data$change_drug_therapy)
# valid cohort
test.table <- CreateTableOne(vars=catvars, strata = "rrt", data = valid.data)
b <- print(test.table, quote = TRUE)[, -4]
g1 <- paste('Non RRT (n=', b[1,1], ')')
g2 <- paste('RRT (n=', b[1,2], ')')
colnames(b) <- c(g1, g2, 'p-value')
b <- b[-1, ]
# write.csv(b, '~/Documents/python-projects/Datathon-DR/report/outcomevariable_summary_valid.csv')
```

###2. Visiualize data

####a.) There are 1217 patients in our dataset, among which 561 add drug dose after diuretic resist, 169 change drug, and 93 of them finally had dialysis.
```{r warning= FALSE, echo = FALSE, message=FALSE}
# table(data.std$change_drug_therapy)
# table(data.std$add_drug_therapy)
# table(data.std$rrt)
x <- c(169, 561, 394, 93)
labels <- c('Change drug\n 169(20.5%)', 'Add drug\n 561(68.2%)', 'Other\n 394(32.4%)', 'Dialysis\n 93(11.3%)')
pie(x, labels, main = 'Therapy applied in diuretic resist patients')
```

####b. ) 247 of them died in hospital. 970 survived

```{r warning= FALSE, echo = FALSE, message=FALSE}
# table(data.std$hospital_expire_flag)
x <- c(247, 970)
labels <- c('Dead\n 247(20.30%)', 'Survived\n 970(79.7%)')
pie(x, labels, main = 'Death percentage in diuretic resist patients')
```

###3. Missing data interpolation
* 1. Case delete for patients with many missing values
* 2. Linear interpolation for lab test values(e.g heart rate after rrt was interpolate use hr on admmission, hr after DR and hr on discharge)

```{r warning= FALSE, echo = FALSE, message=FALSE, results=FALSE, }
# remove time3 related variables: noso..., 
mydata <- data.std[, names(data.std) %in% c('nosocomial_hypoproteinemia', 'nosocomial_anemia', 'nosocomial_hyponatremia', 'total_drug_unit', 'diure_resis_to_rrt_day', 'diure_drug_use_to_rrt_day', 'therapy_to_dis_day') == FALSE]
summary(mydata)
mydata <- DataInterp(mydata)
```


### Apply lasso regression to select variables for logistic regression, use orginal dataset
```{r warning= FALSE, echo = FALSE, message=FALSE}
library(glmnet)
# lasso regression
# =================
data <- mydata
y <- as.numeric(as.character(data$rrt))
# remove outcome variables
x <- data[, names(data) %in% c('hadm_id', 'los_icu', 'los_hos', 'hospital_expire_flag') == FALSE]
# only include variables at admission and DR 
x <- data[, names(data) %in% c('age', 'gender', 'add_drug_therapy', 'change_drug_therapy', 'height', 'weight_adm', 'weight_after_dr', 
'bbr', 'inotropes_vasopressor', 'acei', 'mra', 'vasodilator', 
'ischemic_heart_disease', 'cardiomyopathies', 'valvular_disease', 'atrial_fibrilation', 'hyperlipidemia', 'hypertension', 'diabetes', 'sleep_disordered_breathing', 'renal_failure', 'anemia', 'infection', 'alcohol_abuse',
'hr_adm', 'hr_dr', 'sbp_adm', 'sbp_dr', 'dbp_adm', 'dbp_dr', 'spo2_adm', 'spo2_dr', 'tem_adm', 'tem_dr', 
'base_excess_adm', 'bun_adm', 'bun_dr', 'creatinine_adm', 'creatinine_dr', 'sodium_adm', 'sodium_dr', 'potassium_adm', 'potassium_dr', 'hemoglobin_adm', 'hemoglobin_dr', 'hco3_adm', 'hco3_dr', 'gfr_adm', 'gfr_dr', 'ph_adm', 'ph_dr', 'albumin_adm', 'albumin_dr')]
x[, ] <- lapply(x[, ], as.character)
x[, ] <- lapply(x[, ], as.numeric)
x <- as.matrix(x[, ])

set.seed(999)
fit.lasso <- cv.glmnet(x, y, family='binomial', alpha=1, parallel=TRUE, standardize=TRUE, type.measure='auc')
plot(fit.lasso)
fit.lasso$lambda.min
fit.lasso$lambda.1se
coef(fit.lasso, s=fit.lasso$lambda.min)
# remove variables which coef = 1
# 'change_drug_therapy', 'weight_adm', 'weight_after_dr', 'bbr', 'vasodilator', 'valvular_disease', 'hypertension', 'sleep_disordered_breathing', 'sbp_dr', 'dbp_adm', 'tem_adm', 'creatinine_adm', 'sodium_dr', 'potassium_adm', 'hco3_adm'
```

####Apply logistic regression for all patients, only contain variables on admission and first measurement after DR

```{r warning= FALSE, echo = FALSE, message=FALSE}
data <- mydata
data.model <- data[, names(data) %in% c('age', 'gender', 'add_drug_therapy', 'change_drug_therapy', 'height', 'weight_adm', 'weight_after_dr', 
'bbr', 'inotropes_vasopressor', 'acei', 'mra', 'vasodilator', 
'ischemic_heart_disease', 'cardiomyopathies', 'valvular_disease', 'atrial_fibrilation', 'hyperlipidemia', 'hypertension', 'diabetes', 'sleep_disordered_breathing', 'renal_failure', 'anemia', 'infection', 'alcohol_abuse',
'hr_adm', 'hr_dr', 'sbp_adm', 'sbp_dr', 'dbp_adm', 'dbp_dr', 'spo2_adm', 'spo2_dr', 'tem_adm', 'tem_dr', 
'base_excess_adm', 'bun_adm', 'bun_dr', 'creatinine_adm', 'creatinine_dr', 'sodium_adm', 'sodium_dr', 'potassium_adm', 'potassium_dr', 'hemoglobin_adm', 'hemoglobin_dr', 'hco3_adm', 'hco3_dr', 'gfr_adm', 'gfr_dr', 'ph_adm', 'ph_dr', 'albumin_adm', 'albumin_dr', 'rrt')]
# remove variables in lasso regression
data.model <- data.model[, names(data.model) %in% c('change_drug_therapy', 'weight_adm', 'weight_after_dr', 'bbr', 'vasodilator', 'valvular_disease', 'hypertension', 'sleep_disordered_breathing', 'sbp_dr', 'dbp_adm', 'tem_adm', 'creatinine_adm', 'sodium_dr', 'potassium_adm', 'hco3_adm') == FALSE]

# variables below are selected respect to lasso regression
model1 <- glm(rrt ~ .
              , family = binomial(link = 'logit')
              , data = data.model)
summary(model1)
model2 <- step(model1)
summary(model2)
# summary OR and 95%CI for output 
a <- cbind(exp(coef(model2)), exp(confint(model2)), p_value = coef(summary(model2))[, 4])
b <- round(a, 5)
b <- cbind(paste(b[, 1], '(', b[, 2], ',', b[, 3], ')'), b[, 4])
b <- as.data.frame(b)
rownames(b) <- rownames(a)
colnames(b) <- c('OR (95%CI)', 'p value')
b
write.csv(b, '~/Documents/python-projects/Datathon-DR/report/model_output_first_2_timestamp.csv')
```


Expore relation between rrt and GFR and fluid variables
```{r}
data <- mydata
# lm.gfr <- lm(data$gfr_dis ~., data <- data[, names(data) %in% c('los_icu', 'los_hos', 'hospital_expire_flag', 'weight_dis', 'dr_to_dis_day', 'total_output_to_discharge', 'total_input_to_discharge', 'fluid_overload_to_dis', 'urine_output_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
# lm.gfr2 <- step(lm.gfr)
lm.gfr2 <- lm(data$gfr_dis ~ rrt + age + weight_gain_before_rrt_perday + 
    bbr + acei + vasodilator + ischemic_heart_disease + renal_failure + 
    infection + sbp_adm + spo2_adm + base_excess_adm + bun_therapy + 
    creatinine_therapy + creatinine_dr + sodium_therapy + potassium_adm + 
    hemoglobin_dr + hco3_therapy + gfr_therapy + gfr_adm + gfr_dr + 
    ph_therapy + ph_dr + albumin_adm + albumin_dr
    , data <- data)
summary(lm.gfr2)
a <- cbind(round(coef(lm.gfr2), 2), round(confint(lm.gfr2), 2), p_value = round(coef(summary(lm.gfr2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/gfr_lm_summary.csv')
```
Discoverd that rrt is not a significant variable

Expore relation between rrt and total_output_to_discharge and fluid variables
```{r}
data <- mydata
lm.fb1 <- lm(data$total_output_to_discharge ~., data <- data[, names(data) %in% c('los_icu', 'los_hos', 'hospital_expire_flag', 'weight_dis', 'dr_to_dis_day', 'gfr_dis', 'total_input_to_discharge', 'fluid_overload_to_dis', 'urine_output_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
lm.fb2 <- step(lm.fb1)
summary(lm.fb2)
a <- cbind(round(coef(lm.fb2), 2), round(confint(lm.fb2), 2), p_value = round(coef(summary(lm.fb2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/fb_output_lm_summary.csv')
```

Expore relation between rrt and total_input_to_discharge and fluid variables
```{r}
data <- mydata
# lm.fb1 <- lm(data$total_input_to_discharge ~., data <- data[, names(data) %in% c('los_icu', 'los_hos', 'hospital_expire_flag', 'weight_dis', 'dr_to_dis_day', 'gfr_dis', 'total_output_to_discharge', 'fluid_overload_to_dis', 'urine_output_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
# lm.fb2 <- step(lm.fb1)
# summary(lm.fb2)
lm.fb2 <- lm(formula = data$total_input_to_discharge ~ age + gender + add_drug_therapy + 
    weight_adm + weight_before_dialysis + bmi + weight_gain_before_rrt_perday + 
    inotropes_vasopressor + acei + vasodilator + anemia + infection + 
    fluid_overload_to_rrt + urine_output_to_rrt + hr_dr + sbp_adm + 
    sbp_dr + spo2_adm + bun_adm + creatinine_adm + creatinine_dr + 
    sodium_therapy + sodium_adm + potassium_therapy + potassium_adm + 
    hco3_therapy + hco3_dr + gfr_therapy + gfr_dr + albumin_therapy + 
    albumin_adm + rrt, data = data <- data[, names(data) %in% c("los_icu", 
    "los_hos", "hospital_expire_flag", "weight_dis", "dr_to_dis_day", 
    "gfr_dis", "total_output_to_discharge", "fluid_overload_to_dis", 
    "urine_output_to_dis", "hr_dis", "sbp_dis", "dbp_dis", "spo2_dis", 
    "tem_dis", "bun_dis", "creatinine_dis", "sodium_dis", "potassium_dis", 
    "hemoglobin_dis", "hco3_dis", "ph_dis", "albumin_dis") == 
    FALSE])
a <- cbind(round(coef(lm.fb2), 2), round(confint(lm.fb2), 2), p_value = round(coef(summary(lm.fb2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/fb_input_lm_summary.csv')
```

Expore relation between rrt and fluid_overload_to_discharge and fluid variables
```{r}
data <- mydata
lm.fb1 <- lm(data$fluid_overload_to_dis ~., data <- data[, names(data) %in% c('los_icu', 'los_hos', 'hospital_expire_flag', 'weight_dis', 'dr_to_dis_day', 'gfr_dis', 'total_output_to_discharge', 'total_input_to_discharge', 'urine_output_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
lm.fb2 <- step(lm.fb1)
summary(lm.fb2)
a <- cbind(round(coef(lm.fb2), 2), round(confint(lm.fb2), 2), p_value = round(coef(summary(lm.fb2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/fb_overload_lm_summary.csv')
```

Expore relation between rrt and urine_output_to_discharge and fluid variables
```{r}
data <- mydata
lm.fb1 <- lm(data$urine_output_to_dis ~., data <- data[, names(data) %in% c('los_icu', 'los_hos', 'hospital_expire_flag', 'weight_dis', 'dr_to_dis_day', 'gfr_dis', 'total_output_to_discharge', 'total_input_to_discharge', 'fluid_overload_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
lm.fb2 <- step(lm.fb1)
summary(lm.fb2)
a <- cbind(round(coef(lm.fb2), 2), round(confint(lm.fb2), 2), p_value = round(coef(summary(lm.fb2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/uo_lm_summary.csv')
```

Expore relation between rrt and los hospital
```{r}
data <- mydata
data$los_hos <- data$los_hos/24
lm.los1 <- lm(data$los_hos ~., data <- data[, names(data) %in% c('los_icu', 'urine_output_to_dis', 'hospital_expire_flag', 'weight_dis', 'dr_to_dis_day', 'gfr_dis', 'total_output_to_discharge', 'total_input_to_discharge', 'fluid_overload_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
lm.los2 <- step(lm.los1)
summary(lm.los2)
a <- cbind(round(coef(lm.los2), 2), round(confint(lm.los2), 2), p_value = round(coef(summary(lm.los2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/los_hos_lm_summary.csv')
```

Expore relation between rrt and los ICU
```{r}
data <- mydata
data$los_icu <- data$los_icu/24
lm.los1 <- lm(data$los_icu ~., data <- data[, names(data) %in% c('los_hos', 'urine_output_to_dis', 'hospital_expire_flag', 'weight_dis', 'dr_to_dis_day', 'gfr_dis', 'total_output_to_discharge', 'total_input_to_discharge', 'fluid_overload_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
lm.los2 <- step(lm.los1)
summary(lm.los2)
a <- cbind(round(coef(lm.los2), 2), round(confint(lm.los2), 2), p_value = round(coef(summary(lm.los2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/los_icu_lm_summary.csv')
```

Expore relation between rrt and hospital expire
```{r}
data <- mydata
# glm.death <- glm(data$hospital_expire_flag ~., family = binomial(link = 'logit'), data <- data[, names(data) %in% c('los_hos', 'urine_output_to_dis', 'los_icu', 'weight_dis', 'dr_to_dis_day', 'gfr_dis', 'total_output_to_discharge', 'total_input_to_discharge', 'fluid_overload_to_dis', 'hr_dis', 'sbp_dis', 'dbp_dis', 'spo2_dis', 'tem_dis', 'bun_dis', 'creatinine_dis', 'sodium_dis', 'potassium_dis', 'hemoglobin_dis', 'hco3_dis', 'ph_dis', 'albumin_dis') == FALSE])
# glm.death2 <- step(glm.death)
glm.death2 <- glm(data$hospital_expire_flag ~ rrt + age + gender + add_drug_therapy + change_drug_therapy + height + weight_adm + weight_after_dr + weight_before_dialysis + weight_gain_before_rrt + bbr + inotropes_vasopressor + acei + mra + vasodilator + alcohol_abuse + daily_uo_to_rrt + hr_therapy + hr_adm + spo2_adm + tem_therapy + bun_therapy + bun_adm + creatinine_therapy + sodium_therapy + sodium_adm + potassium_therapy + hco3_therapy + ph_dr + albumin_dr
    , family = binomial(link = 'logit')
    , data <- data)
summary(glm.death2)
a <- cbind(round(exp(coef(glm.death2)), 2), round(exp(confint(glm.death2)), 2), p_value = round(coef(summary(glm.death2))[, 4], 4))
b <- cbind(paste(a[, 1], '(', a[, 2], ',', a[, 3], ')'), a[, 4])
b <- as.data.frame(b)
colnames(b) <- c('coef(95%CI)', 'p value')
b$`p value` <- as.character(b$`p value`)
b[which(b$`p value` == 0), 2] <- c('< 0.0001')
# write.csv(b, '~/Desktop/hos_expire_glm_summary.csv')
```
