---
title: "DR analysis"
output: html_document
---

```{r}
source('~/Documents/python-projects/Datathon-DR/scr/R/help.R')
```

```{r load data, warning=FALSE, echo=FALSE, message=FALSE}
library(readr)
basic_info <- read_csv("~/Documents/python-projects/Datathon-DR/data/basic_info.csv")

# age above 300 need to convert
basic_info$age[basic_info$age >= 300] <- 90
basic_info[, c("gender", "add_drug_therapy", "change_drug_therapy", "total_drug_unit", "rrt")][is.na(basic_info[, c("gender", "add_drug_therapy", "change_drug_therapy", "total_drug_unit", "rrt")])] <- 0
# remove timestamp data
basic_info <- basic_info[, -c(1, 5, 6, 8, 10, 11, 13:15, 19, 21)]
# convert binary variable to factor
basic_info$gender[which(basic_info$gender == 'F')] <- 0
basic_info$gender[which(basic_info$gender == 'M')] <- 1
basic_info[, c(3, 4, 7, 8, 10)] <- lapply(basic_info[, c(3, 4, 7, 8, 10)], as.factor)

# drug use data 
druguse <- read_csv("~/Documents/python-projects/Datathon-DR/data/druguse.csv")[, -1]
druguse[, c(2:18)] <- lapply(druguse[, c(2:18)], as.factor)

# nosocomial data by caoyang
nosocomial <- read_csv("~/Documents/python-projects/Datathon-DR/data/nosocomial.csv")[, -c(1, 3:5)]
nosocomial[is.na(nosocomial)] <- 0
nosocomial[, c(2:4)] <- lapply(nosocomial[, c(2:4)], as.factor)

# fluid load data
fluidload <- read_csv("~/Documents/python-projects/Datathon-DR/data/fluidload.csv")[, -1]

# vital data
vital <- read_csv("~/Documents/python-projects/Datathon-DR/data/vital.csv")[, -1]

# lab test
lab <- read_csv("~/Documents/python-projects/Datathon-DR/data/lab.csv")[, -c(14, 27, 40)]
lab[, c(1:49)] <- lapply(lab[, c(1:49)], as.numeric)
names(lab)[49] <- 'bun_dis' # wrong name of bun on discharge
```

```{r merge data, warning=FALSE, echo=FALSE, message=FALSE}
data.raw <- merge(basic_info, druguse, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, fluidload, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, nosocomial, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, vital, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
data.raw <- merge(data.raw, lab, by.x = 'hadm_id', by.y = 'hadm_id', all.x = TRUE)
```

###Preprocess -- missing values
* 1. ) several patients may have wrong weight values, since they are no-RRT patients, remove them entirly
* 2. ) cvp have many missing values( > 863/1271), so do urine_acid, bnp and base excess(this one exclude admission), better remove them before analysis.
* 3. ) And the third timestamp(get better date) have about a half missing data, for more then 500 no-rrt patients can't find a urine increase time according to the definition. This may cause bias, but analysis below will still include these variables.

```{r warning=FALSE, echo=FALSE, message=FALSE}
# final dataset
# remove cvp, urine acid, bnp and base excess(not adm)
data.std <- data.raw[, -c(65:68, 74, 78, 86, 87, 90, 98, 99, 102, 110, 111, 114)]
```

###1. Baseline characteristics, stratified by rrt

```{r warning=FALSE, echo=FALSE, message=FALSE}
# create baseline summary
library(tableone)
catvars <- c("age", "gender", "height", "weight_adm","bmi", "bbr", "inotropes_vasopressor", "acei", "mra", "vasodilator", "ischemic_heart_disease", "cardiomyopathies", "valvular_disease", "atrial_fibrilation", "hyperlipidemia", "hypertension", "diabetes", "sleep_disordered_breathing", "renal_failure", "anemia", "infection", "alcohol_abuse", "hr_adm", "sbp_adm", "dbp_adm", "spo2_adm", "tem_adm", "gfr_adm", "bnp_adm", "base_excess_adm", "hco3_adm", "ph_adm", "urine_acid_adm", "hemoglobin_adm", "albumin_adm", "potassium_adm", "sodium_adm", "creatinine_adm", "bun_adm") 
test.table <- CreateTableOne(vars=catvars, strata = "rrt", data = data.std)
a <- print(test.table, quote = TRUE)[, -4]
g1 <- paste('Non RRT (n=', a[1,1], ')')
g2 <- paste('RRT (n=', a[1,2], ')')
colnames(a) <- c(g1, g2, 'p-value')
a <- a[-1, ]
# write.csv(a, '~/Documents/python-projects/Datathon-DR/report/baseline_analysis.csv')
```

###2. Characteristics of fluid value and outcomes

```{r}
catvars <- c("los_hos", "los_icu", "hospital_expire_flag", "add_drug_therapy", "change_drug_therapy", "fluid_overload_to_rrt", "daily_fluid_overload_to_rrt", "urine_output_to_rrt", "daily_uo_to_rrt", "total_input_to_discharge", "total_output_to_discharge", "fluid_overload_to_dis", "urine_output_to_dis") 
test.table <- CreateTableOne(vars=catvars, strata = "rrt", data = data.std)
a <- print(test.table, quote = TRUE)[, -4]
g1 <- paste('Non RRT (n=', a[1,1], ')')
g2 <- paste('RRT (n=', a[1,2], ')')
colnames(a) <- c(g1, g2, 'p-value')
a <- a[-1, ]
# write.csv(a, '~/Documents/python-projects/Datathon-DR/report/outcomevariable_summary.csv')
```

###2. Visiualize data

####a.) There are 1217 patients in our dataset, among which 561 add drug dose after diuretic resist, 169 change drug, and 93 of them finally had dialysis.
```{r warning= FALSE, echo = FALSE, message=FALSE}
# table(data.std$change_drug_therapy)
# table(data.std$add_drug_therapy)
# table(data.std$rrt)
x <- c(169, 561, 394, 93)
labels <- c('Change drug\n 169(20.5%)', 'Add drug\n 561(68.2%)', 'Other\n 394(32.4%)', 'Dialysis\n 93(11.3%)')
pie(x, labels, main = 'Therapy applied in diuretic resist patients')
```

####b. ) 247 of them died in hospital. 970 survived

```{r warning= FALSE, echo = FALSE, message=FALSE}
# table(data.std$hospital_expire_flag)
x <- c(247, 970)
labels <- c('Dead\n 247(20.30%)', 'Survived\n 970(79.7%)')
pie(x, labels, main = 'Death percentage in diuretic resist patients')
```

###3. Missing data interpolation
* 1. Case delete for patients with many missing values
* 2. Linear interpolation for lab test values(e.g heart rate after rrt was interpolate use hr on admmission, hr after DR and hr on discharge)

```{r warning= FALSE, echo = FALSE, message=FALSE, results=FALSE, }
# first deal with missing data
mydata <- DataInterp(data.std)
summary(mydata)
```

###In our dataset, rrt : no-rrt is almost 1:10, it's very unbalanced. 
####Several methods can be applied to handle a unbalanced dataset, including oversampling, downsampling, synthetic method etc.
```{r warning= FALSE, echo = FALSE, message=FALSE}
library(ROSE)
# use oversampling to handle unbalanced data
mydata.rose1 <- ovun.sample(rrt ~ ., data = mydata[, -1], method = "over")$data
# table(mydata.rose1$rrt)
mydata.rose2 <- ovun.sample(rrt ~ ., data = mydata[, -1], method = "both")$data
# table(mydata.rose0$rrt)
mydata.rose3 <- ROSE(rrt ~., data = mydata[, -1], seed = 1)$data
# table(mydata.rose2$rrt)
mydata.rose0 <- ovun.sample(rrt ~ ., data = mydata[, -1], method = "under" )$data
# table(mydata.rose0$rrt)
```

###Use random forest to see if the two cluster can be seperate
####While the first pic applied oversampling method, the second is sampled data use synthetic data sampling method
####The first may have overfitting issuse!
```{r warning= FALSE, echo = FALSE, message=FALSE}
library(randomForest)
mydata.rose1$rrt <- as.factor(mydata.rose1$rrt)
set.seed(1234)
# mydata.rf <- randomForest(rrt~.,data = mydata.rose1, ntree = 500, importance = TRUE)
# importance(mydata.rf)
mydata.rf <- randomForest(rrt~.,data = mydata.rose0, proximity = TRUE)

MDSplot(mydata.rf, mydata.rose0$rrt, palette = c('blue', 'orange'), pch = as.numeric(mydata.rose0$rrt))

# up&over sampling method
mydata.rose2$rrt <- as.factor(mydata.rose3$rrt)
mydata.rf <- randomForest(rrt~.,data = mydata.rose3, proximity = TRUE)

MDSplot(mydata.rf, mydata.rose3$rrt, palette = c('blue', 'orange'), pch = as.numeric(mydata.rose3$rrt))
```

### Use PCA to deduct dimension
####It's not clear that rrt and no-rrt can be seperate.
####Here's rouse a question, is PCA proper to show the distinguish of clusters?
```{r warning= FALSE, echo = FALSE, message=FALSE}
pca.data <- mydata
pca.data[,-1] <- lapply(pca.data[,-1], as.character)
pca.data[,-1] <- lapply(pca.data[,-1], as.numeric)

mydata.pr2 <- prcomp(pca.data[, -1], scale. = T)
mydata.existing.df2 <- as.data.frame(mydata.pr2$x)

library(ggplot2)
test.data2 <- cbind(pca.data, mydata.existing.df2[1:2])
ggplot(test.data2, aes(x = PC1, y = PC2, group = rrt)) + 
  geom_point(aes(colour = factor(rrt))) +
  ggtitle('Scatter plot of two main components')

pca.data2 <- mydata.rose1
pca.data2[, ] <- lapply(mydata.rose1, as.character)
pca.data2[, ] <- lapply(pca.data2, as.numeric)

mydata.pr <- prcomp(pca.data2[, -1], scale. = T)
mydata.df <- as.data.frame(mydata.pr$x)
test.data <- cbind(mydata.rose1, mydata.df[1:2])
ggplot(test.data, aes(x = PC1, y = PC2, group = rrt)) + 
  geom_point(aes(colour = factor(rrt))) +
  ggtitle('Scatter plot of two main components, after oversampling')

pca.data3 <- mydata.rose2
pca.data3[, ] <- lapply(mydata.rose2[, ], as.character)
pca.data3[, ] <- lapply(pca.data2[, ], as.numeric)

mydata.pr <- prcomp(pca.data3, scale. = T)
mydata.df <- as.data.frame(mydata.pr$x)
test.data <- cbind(mydata.rose2, mydata.df[1:2])
ggplot(test.data, aes(x = PC1, y = PC2, group = rrt)) + 
  geom_point(aes(colour = factor(rrt))) +
  ggtitle('Scatter plot of two main components, after up and over sampling')

pca.data4 <- mydata.rose3
pca.data4[, ] <- lapply(mydata.rose3[, ], as.character)
pca.data4[, ] <- lapply(pca.data3[, ], as.numeric)

mydata.pr <- prcomp(pca.data4, scale. = T)
mydata.df <- as.data.frame(mydata.pr$x)
test.data <- cbind(mydata.rose3, mydata.df[1:2])
ggplot(test.data, aes(x = PC1, y = PC2, group = rrt)) + 
  geom_point(aes(colour = factor(rrt))) +
  ggtitle('Scatter plot of two main components, after artifically sampling')

pca.data5 <- mydata.rose0
pca.data5[, ] <- lapply(mydata.rose0[, ], as.character)
pca.data5[, ] <- lapply(pca.data5[, ], as.numeric)

mydata.pr <- prcomp(pca.data5, scale. = T)
mydata.df <- as.data.frame(mydata.pr$x)
test.data <- cbind(mydata.rose0, mydata.df[1:2])
ggplot(test.data, aes(x = PC1, y = PC2, group = rrt)) + 
  geom_point(aes(colour = factor(rrt))) +
  ggtitle('Scatter plot of two main components, after up sampling')
```

### Apply lasso regression to select variables for linear regression, use orginal dataset
```{r warning= FALSE, echo = FALSE, message=FALSE}
library(glmnet)
# lasso regression
# =================
data <- data.std[!is.na(data.std$nosocomial_anemia),]
data <- DataInterp(data)
data <- train.data
y <- as.numeric(as.character(data$rrt))
x <- data[, c('age',  'gender',  'add_drug_therapy',  'change_drug_therapy',  'total_drug_unit',  'height',  'weight_adm',  'weight_after_dr',  'weight_before_dialysis',  'weight_gain_before_rrt',  'weight_gain_before_rrt_perday',  'bbr',  'inotropes_vasopressor',  'acei',  'mra',  'vasodilator',  'ischemic_heart_disease',  'cardiomyopathies',  'valvular_disease',  'atrial_fibrilation',  'hyperlipidemia',  'hypertension',  'diabetes',  'sleep_disordered_breathing',  'renal_failure', 'anemia',  'alcohol_abuse',  'nosocomial_hypoproteinemia',  'nosocomial_anemia', 'nosocomial_hyponatremia',  'fluid_overload_to_rrt',  'daily_fluid_overload_to_rrt',  'urine_output_to_rrt',  'daily_uo_to_rrt',  'hr_adm',  'hr_therapy',  'hr_dr',  'sbp_adm',  'sbp_therapy',  'sbp_dr',  'dbp_adm',  'dbp_therapy',  'dbp_dr',  'spo2_adm',  'spo2_dr',  'spo2_therapy',  'tem_adm',  'tem_dr',  'tem_therapy',  'base_excess_adm',  'bun_adm',  'creatinine_adm',  'creatinine_dr',  'creatinine_therapy',  'sodium_adm',  'sodium_dr',  'sodium_therapy',  'potassium_adm',  'potassium_dr',  'potassium_therapy',  'hemoglobin_adm',  'hemoglobin_dr',  'hemoglobin_therapy',  'hco3_adm',  'hco3_dr',  'hco3_therapy',  'gfr_adm',  'gfr_dr',  'gfr_therapy',  'ph_adm',  'ph_dr',  'ph_therapy',  'albumin_adm',  'albumin_dr',  'albumin_therapy')]
x <- data[, -c(1, 10)]
x[, ] <- lapply(x[, ], as.character)
x[, ] <- lapply(x[, ], as.numeric)
x <- as.matrix(x[, ])

set.seed(999)
fit.lasso <- cv.glmnet(x, y, family='binomial', alpha=1, parallel=TRUE, standardize=TRUE, type.measure='auc')
plot(fit.lasso)
fit.lasso$lambda.min
fit.lasso$lambda.1se
coef(fit.lasso, s=fit.lasso$lambda.min)
```

####Apply linear regression for all patients, exclude variables related to the third timestamp
```{r warning= FALSE, echo = FALSE, message=FALSE}
# model1 <- glm(rrt ~ age + gender + add_drug_therapy + change_drug_therapy + total_drug_unit + height + weight_adm + weight_after_dr + weight_before_dialysis + weight_gain_before_rrt_perday + bbr +  inotropes_vasopressor + acei + mra + vasodilator + ischemic_heart_disease + cardiomyopathies + valvular_disease + atrial_fibrilation + hyperlipidemia + hypertension + diabetes + sleep_disordered_breathing + renal_failure + anemia + alcohol_abuse + nosocomial_hypoproteinemia + nosocomial_anemia + nosocomial_hyponatremia + fluid_overload_to_rrt + daily_fluid_overload_to_rrt + urine_output_to_rrt + daily_uo_to_rrt + hr_adm + hr_therapy + hr_dr + sbp_adm + sbp_therapy + sbp_dr + dbp_adm + dbp_therapy + dbp_dr + spo2_adm + spo2_dr + spo2_therapy + tem_adm + tem_dr + tem_therapy + base_excess_adm + bun_adm + creatinine_adm + creatinine_dr + creatinine_therapy + sodium_adm + sodium_dr + sodium_therapy + potassium_adm + potassium_dr + potassium_therapy + hemoglobin_adm + hemoglobin_dr + hemoglobin_therapy + hco3_adm + hco3_dr + hco3_therapy + gfr_adm + gfr_dr + gfr_therapy + ph_adm + ph_dr + ph_therapy + albumin_adm + albumin_dr + albumin_therapy
#               , family = binomial(link = 'logit')
#               , data = mydata)
# summary(model1)
# model2 <- step(model1)
model2 <- glm(rrt ~ gender + add_drug_therapy + weight_adm + 
    weight_after_dr + weight_gain_before_rrt_perday + acei + 
    mra + vasodilator + atrial_fibrilation + hyperlipidemia + 
    renal_failure + nosocomial_hypoproteinemia + nosocomial_anemia + 
    nosocomial_hyponatremia + urine_output_to_rrt + daily_uo_to_rrt + 
    hr_therapy + hr_dr + sbp_therapy + dbp_adm + tem_therapy + 
    sodium_therapy + potassium_therapy + hemoglobin_adm + hco3_dr + 
    gfr_dr + gfr_therapy
              , family = binomial(link = 'logit')
              , data = mydata)
summary(model2)
# summary OR and 95%CI for output 
a <- cbind(exp(coef(model2)), exp(confint(model2)), p_value = coef(summary(model2))[, 4])
b <- round(a, 5)
b <- cbind(paste(b[, 1], '(', b[, 2], ',', b[, 3], ')'), b[, 4])
b <- as.data.frame(b)
rownames(b) <- rownames(a)
colnames(b) <- c('OR (95%CI)', 'p value')
b
# write.csv(b, '~/Documents/python-projects/Datathon-DR/report/model_output.csv')
```



Use random forest to pretict

At first the result is so good, so I examine the dataset, notice that variables on the third timestamp have many missings for non-rrt patients(about 500 patients cann't defined this time). In classification, do not include these variables.

```{r}
library(randomForest)
library(pROC)
library(ROCR)
library(dplyr)
data <- data.std[!is.na(data.std$nosocomial_anemia),]
data <- DataInterp(data)
train.data <- sample_frac(data, 0.7)
test.data <- anti_join(data, train.data)
train.data <- DataInterp(train.data)
test.data <- DataInterp(test.data)
# summary(train.data$rrt)
# summary(test.data$rrt)

rf <- randomForest(rrt ~ creatinine_therapy + gfr_therapy + spo2_adm + bun_therapy + urine_output_to_discharge
               , data = train.data[, -c(1, 4:6)], ntree=100, proximity=TRUE,importance=TRUE)  
importance(rf)
varImpPlot(rf, n.var = 20, main = 'Variable importance, Random Forest')

test.data$pred2 <- predict(rf, test.data, type = 'prob')
rocobj1 <- plot.roc(test.data$rrt,
                      test.data$pred2[, 2],
                      percent=TRUE,ci=TRUE,col="#1c61b6",
                      print.auc=TRUE)

pred3 <- predict(rf, test.data)
z <- table(predict(rf, test.data), test.data$rrt)
q <- sum(diag(z))/sum(z)
```

Test logistic regression 
```{r}
result <- RegressionAndPredict(train.data, test.data, 'rrt')
result
```

